Finding Bugs in JavaScript Engines with Differential Testing

### 2018-05-14 docs/google-research-awards-latam/main.tex
pass on results

    Contact at Google:~Martin Barbella (mbarbella@google.com) and Vilas Jagannath (vilasshekharbj@gmail.com)

@@

The basic workflow described in Section~\ref{sec:design} is functional. This section shows preliminary
results obtained with our infrastructure providing some evidence that finding bugs in runtime engines is
promising. Table~\ref{tab:bugs} shows the list of bugs we reported on
issue trackers of different engines in the period of a month. For
example, bug \# 6 was manifested by the JS code \CodeIn{var a =
  \{valueOf:~function()\{return ``\textbackslash{}x00''\}\} assert(+a
  === 0)\}}. 
\Igor{
  The \CodeIn{valueOf} is an object property that returns the primitive value
  of the specific object\cite{valueof} and in the original version of this code,
  the \CodeIn{valueOf} function returns an empty string.
  The modified code returns a string representation of an embedded null terminator
  value. 
  The unary plus ``\CodeIn{+a}" is equivalent to \CodeIn{String.ToNumber(a.valueOf())} 
  that converts a variable to a number, but if the value cannot be converted, 
  the return should be the value NaN (Not a Number) \cite{unary-plus}.
  As such, the engines evaluate that unary plus as a NaN value 
  at the assertion expression; hence test execution is expected to fail. 
  Chakra, however, is able to parse the string as a number zero, making the test to pass.
}
\newcommand{\checkm}{Y}
\newcommand{\crossmark}{N}
\begin{wraptable}[20]{tr}[0pt]{0.5\textwidth}
  \vspace{-2ex}
  \scriptsize
  \centering
  \caption{List of bug reports issued by our team from April 12 to May
    10, 2018.}
  \label{tab:bugs}
  \begin{tabular}{cccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}   \\
    \midrule    
    1  & 4/12 & \checkm & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
    2  & 4/12 & \checkm & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
    3  & 4/14 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
    6  & 4/25 & \checkm & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
                        & \checkm &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
    \midrule    
    9  & 4/29 & \checkm & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{\checkm} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
    \\
    \midrule    
    11 & 5/02 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
    13 & 5/10 & \crossmark & Chakra & New & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
   \bottomrule     
  \end{tabular}
\end{wraptable}

>>>>

    Contact at Google:~Martin Barbella (mbarbella@google.com)

@@

The basic workflow described in Section~\ref{sec:design} is functional. This section shows preliminary
results obtained with our infrastructure providing some evidence that finding bugs in runtime engines is
promising. Table~\ref{tab:bugs} shows the list of bugs we reported on
issue trackers of different engines in the period of a month. For
example, bug \# 6 was manifested by the JS code \CodeIn{var a =
  \{valueOf:~function()\{return ``\textbackslash{}x00''\}\} assert(+a
  === 0)\}}. 
\Igor{
  The \CodeIn{valueOf} function is a primitive value of
  a String object and in the original version of this code,
  the \CodeIn{valueOf} function returns an empty string.
  The modified code returns a string representation of an embedded null terminator
  value. 
  The unary plus\cite{unary-plus} ``\CodeIn{+a}" in this case is equivalent to 
  \CodeIn{String.ToNumber(a.valueOf())} that
  converts a variable to a number, but if 
  the value cannot be converted, the return should be the value NaN (Not a Number).
  As such, the engines evaluate that unary plus as a NaN value 
  at the assertion expression; hence test execution is expected to fail. 
  Chakra, however, is able to parse the string as a number zero, making the test to pass.
}
\newcommand{\checkm}{Y}
\newcommand{\crossmark}{N}
\begin{wraptable}[20]{tr}[0pt]{0.5\textwidth}
  \vspace{-2ex}
  \scriptsize
  \centering
  \caption{List of bug reports issued by our team from April 12 to May
    10, 2018.}
  \label{tab:bugs}
  \begin{tabular}{cccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}   \\
    \midrule    
    1  & 4/12 & \checkm & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
    2  & 4/12 & \checkm & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
    3  & 4/14 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
    6  & 4/25 & \checkm & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
                        & \checkm &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
    \midrule    
    9  & 4/29 & \checkm & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{\checkm} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
    \\
    \midrule    
    11 & 5/02 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
    13 & 5/10 & \crossmark & Chakra & New & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
   \bottomrule     
  \end{tabular}
\end{wraptable}
